Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-31 msbr_reproc.tex
grammar

Currently, researchers 
investigating the \glspl{MSR} 
typically develop custom supporting tools and scripts to simulate 
online reprocessing and refueling. Most utilize stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) methods for depletion and supplement 
these with custom Python scripts to capture the impacts of reprocessing 
\cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
first commonly used monte carlo software to support continuous material 
reprocessing. It does so by allowing the user to 
create multiple material flows into and out of the fuel.

@@

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
state with fully withdrawn control and poison rods position which gives high 
excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

@@

Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. The 
high standard deviation causes the multiplication factor fluctuations. 
Protactinium-233 continuously removing into the tank for protactinium decay. 
$^{233}$Pa has a half-life of 27 days and beta decays into $^{233}$U which as 
fresh fuel goes back to the reactor core. The infinite multiplication factor 
decreases first 400 days of depletion due to strong absorbers (e.g. $^{233}$Th, 
$^{234}$U) accumulation which causes relatively high fuel ($^{233}$U) refill 
inflow to keep reactor critical. During reactor operation producing fissile 
materials other than $^{233}$U in the core (e.g. $^{235}$U, $^{239}$Pu) which 
makes it possible to decrease fresh fuel refill rate after ~1 year of 
operation.

@@

The analysis of the fuel salt composition variation gives clearer information 
about equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
number density of important isotopes that have strong influence on the core 
neutronics at the beginning of each depletion time interval. The number density 
of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
of it produced during 3-days reprocessing step. It can be seen that the 
multiplication factor reaches the equilibrium state at about 950  days. 
Figure~\ref{fig:rates} represents the rates of materials in online reprocessing 
flows during 4 years of depletion calculations. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\captionsetup[table]{
%  labelsep = newline,
%  name = TABLE, justification=justified,
%  singlelinecheck=false,%%%%%%% a single line is centered by default
%  labelsep=colon,%%%%%%
%  skip = \medskipamount}
%\begin{table}[h!]
%\centering
%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
%      Isotope & First 400 days     & After 400 days          
%\\ \midrule
%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
%\\
%\bottomrule
%\end{tabular}
%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
%  [1/s*cm$^3$].}
%  \label{tab:rates}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{rates_fuel.png}
        \caption{Materials flows rates during online reprocessing.}
        \label{fig:rates}
\end{figure}
From the graph below we can see that to keep reactor critical higher $^{233}$U 
flow rate required for first 400 days of operation and after that much smaller 
uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th 
rate slightly decreases over 4 years of operation due to other than $^{233}$U 
fissile materials accumulation.

>>>>

Currently, researchers 
investigating the \glspl{MSR} 
typically develop custom supporting tools and scripts to simulate 
online reprocessing and refueling. Most utilize stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) methods for depletion and supplement 
these with custom Python scripts to capture the impacts of reprocessing 
\cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
first commonly used monte carlo software to support continuous material 
reprocessing. It does so by allowing the user to 
define multiple material flows into and out of the fuel. This work applies this 
Serpent 2 feature to the \gls{MSBR}.

@@

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
state with fully withdrawn control and poison rods position which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

@@

Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. A 
significant standard deviation (100 pcm) causes the multiplication factor 
fluctuations visible in this plot.  Protactinium-233 continuously removing into 
the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
The infinite multiplication factor decreases first 400 days of depletion due to 
strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
reactor operation producing fissile materials other than $^{233}$U in the core 
(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
refill rate after ~1 year of operation.

@@

The analysis of the fuel salt composition variation gives clearer information 
about the equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
number density of isotopes influential to core 
neutronics at the beginning of each depletion time interval. The number density 
of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
of it is produced during the 3-day reprocessing period. In this assessment, the multiplication 
factor stabilizes after approximately 950 days. 
Figure~\ref{fig:rates} represents the rates of online reprocessing material flows
flows over the 4-year depletion calculation. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\captionsetup[table]{
%  labelsep = newline,
%  name = TABLE, justification=justified,
%  singlelinecheck=false,%%%%%%% a single line is centered by default
%  labelsep=colon,%%%%%%
%  skip = \medskipamount}
%\begin{table}[h!]
%\centering
%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
%      Isotope & First 400 days     & After 400 days          
%\\ \midrule
%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
%\\
%\bottomrule
%\end{tabular}
%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
%  [1/s*cm$^3$].}
%  \label{tab:rates}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{rates_fuel.png}
        \caption{Materials flows rates during online reprocessing.}
        \label{fig:rates}
\end{figure}
From the graph below we can see that to keep reactor critical higher $^{233}$U 
flow rate required for first 400 days of operation and after that much smaller 
uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th 
rate slightly decreases over 4 years of operation due to other than $^{233}$U 
fissile materials accumulation.
